\documentclass[10pt]{report}
\begin{document}
\title{
{ REPORT ON THE ADVENTURE OF MIDNIGHT SWIMMING}\\
{\large MAKERERE UNIVERSITY}\\
{\large COLLEGE OF COMPUTING AND INFORMATION SCIENCES}
{\large BACHELOR OF SCIENCE IN COMPUTER SCIENCE}
{TABLE OF CONTENTS}\\
{\large Abstraction.......................2}\\
{\large Introduction.......................2}\\
{\large Methodology.......................2}\\
{\large Results..............................2}\\
{\large Conclusion..........................2}\\
{\large Recommendation..................2}}
\author{
{MAGERO TIMOTHY}
{15/U/7629/PS}}
\maketitle


\section{ADVENTURE OF MIDNIGHT SWIMMING}
\subsection{ABSTRACT}
{The aim of this report was to explore this adventure of midnight swimming. The results indicate that its one thing worth doing. I mainly used sampling method by going directly there to explore the adventure myself. I later recommended it to many people because its not only healthy but also fun.}
\subsection{INTRODUCTION}
{Midnight swimming is an activity that takes place once in every week of the semester at Nkrumah hall. It mainly involves residents and non-residents and always takes place at midnight late in the night. The purpose of this is to always bring us together, strengthen our solidarity and improve our health. It mainly involves naked milling that is running fully naked all around the campus.}
\subsection{METHODOLOGY}
{First its always every Friday night of the week where students start by jazzing at the main entrance of Nkrumah hall around 9pm. At around midnight, they start yelling loudly with Nkrumah slogans like Eeeehhhh Nkrumah oyeeeeee to alert their colleagues to join the trend. 
We always start with jogging naked around campus loudly praising the mighty Nkrumah hall after which we trespass into the university swimming pool to conclude the night. }
\subsection{FINDINGS}
{As I conducted my research, I found out that many people especially residents of Nkrumah hall are always taken up by this activity and according to my research the number of students increases by 100 every time the activity is held.}

\subsection{CONCLUSION}
{I concluded that it was worth enjoying and fun to account for that one time night in Nkrumah hall at Makerere University.}
\subsection{RECOMMENDATIONS}
{I strongly recommend students from other halls like Mary Stuart or Africa halls to take part in such activity because its not only fun and enjoyment but also healthy and keeps us physically fit.}
 


\end{document}